Feature Selection - Boruta

### 2020-02-20 poc/matchIt/feature_selection.Rmd
udating feature selection

@@

set.seed(1234)
df_train_sm <- df_train_encoder %>%
   sample_n(1000)

df_fs <- df_train_sm %>%
   select(-engagement) %>%
   select(-content_crashes) %>%
   select(-client_id) %>%
   select(-label_beta) %>%
   select(-label_release) %>%
   select(-is_release) %>%
   select(-app_version)
```

@@

```{r apply_boruta}
boruta_results <- list()
for (metric in engagement){
  print(paste('Applying Boruta to ', metric))
  boruta.out <- Boruta(y = df_train_sm[[metric]], x=df_fs, doTrace=0)
  boruta_results[[metric]]  <- boruta.out
  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r boruta_plots}
for (metric in names(boruta_results)){
  plot(boruta_results[[metric]], cex.axis=.7, las=2, xlab="", main=metric) 
}
```

@@

```{r aggregate_features_5}
features_top5 <- NULL
for(metric in names(boruta_results)){
  features_top5 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}
knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
```

@@

```{r aggregate_features_10}
features_top10 <- NULL
for(metric in names(boruta_results)){
  features_top10 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}
knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
```

@@

Equalize by label, then perform the above.

@@

```{r aggregate_features_5_eq}
features_top5 <- NULL
for(metric in names(boruta_results_eq)){
  features_top5 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}
knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
```

@@

```{r aggregate_features_10_eq}
features_top10 <- NULL
for(metric in names(boruta_results_eq)){
  features_top10 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}
knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
```

>>>>

```{r}
filter_features <- function(df_train_sm){
  df_fs <- df_train_sm %>%
   select(-engagement) %>%
   select(-content_crashes) %>%
   select(-client_id) %>%
   select(-label_beta) %>%
   select(-label_release) %>%
   select(-is_release) %>%
   select(-app_version)
  return(df_fs)
}
```

@@

df_train_sm_1 <- df_train_encoder %>%
   sample_n(1000)
df_train_sm_2 <- df_train_encoder %>%
   sample_n(1000)
df_train_sm_3 <- df_train_encoder %>%
   sample_n(1000)
#df_train_sm_4 <- df_train_encoder %>% sample_n(1000)
#df_train_sm_5 <- df_train_encoder %>% sample_n(1000)

df_fs_1 <- filter_features(df_train_sm_1)
df_fs_2 <- filter_features(df_train_sm_2)
df_fs_3 <- filter_features(df_train_sm_3)
#df_fs_4 <- filter_features(df_train_sm_4)
#df_fs_5 <- filter_features(df_train_sm_5)

```

@@

```{r apply_boruta}
boruta_results_1 <- list()
boruta_results_2 <- list()
boruta_results_3 <- list()
#boruta_results_4 <- list()
#boruta_results_5 <- list()

for (metric in engagement){
  print(paste('Applying Boruta to ', metric))
  boruta.out <- Boruta(y = df_train_sm_1[[metric]], x=df_fs_1, doTrace=0)
  boruta_results_1[[metric]]  <- boruta.out

  boruta.out <- Boruta(y = df_train_sm_2[[metric]], x=df_fs_2, doTrace=0)
  boruta_results_2[[metric]]  <- boruta.out

  boruta.out <- Boruta(y = df_train_sm_3[[metric]], x=df_fs_3, doTrace=0)
  boruta_results_3[[metric]]  <- boruta.out
  #boruta.out <- Boruta(y = df_train_sm_4[[metric]], x=df_fs_4, doTrace=0)
  #boruta_results_4[[metric]]  <- boruta.out
  #boruta.out <- Boruta(y = df_train_sm_5[[metric]], x=df_fs_5, doTrace=0)
  #boruta_results_5[[metric]]  <- boruta.out
}
```

```{r boruta_plots, fig.height=7, fig.width=15}
for (metric in engagement){
  plot(boruta_results_1[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
  plot(boruta_results_2[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
  plot(boruta_results_3[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
}
```

@@

```{r aggregate_features_5}
features_top5_1 <- NULL
features_top5_2 <- NULL
features_top5_3 <- NULL

for(metric in engagement){
  features_top5_1 <- c(names(sort(apply(boruta_results_1[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5_1)
  features_top5_2 <- c(names(sort(apply(boruta_results_2[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5_2)
  features_top5_3 <- c(names(sort(apply(boruta_results_3[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5_3)
}

top5_1 <- sort(c(unique(features_top5_1)))
top5_2 <- sort(c(unique(features_top5_2)))
top5_3 <- sort(c(unique(features_top5_3)))

n <- max(length(top5_1), length(top5_2), length(top5_3))
length(top5_1) <- n 
length(top5_2) <- n 
length(top5_3) <- n

x <- data.frame(top5_1, top5_2, top5_3)
kable(x) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

@@

```{r aggregate_features_10}
features_top10_1 <- NULL
features_top10_2 <- NULL
features_top10_3 <- NULL

for(metric in engagement){
  features_top10_1 <- c(names(sort(apply(boruta_results_1[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10_1)
  features_top10_2 <- c(names(sort(apply(boruta_results_2[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10_2)
  features_top10_3 <- c(names(sort(apply(boruta_results_3[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10_3)
}

top10_1 <- sort(c(unique(features_top10_1)))
top10_2 <- sort(c(unique(features_top10_2)))
top10_3 <- sort(c(unique(features_top10_3)))

n <- max(length(top10_1), length(top10_2), length(top10_3))
length(top10_1) <- n 
length(top10_2) <- n 
length(top10_3) <- n

x <- data.frame(top10_1, top10_2, top10_3)
kable(x) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

@@

As we can see, using different samples hardly changes the result. Therefore, we can use only one df with 1000 samples.
Equalize by label, then perform the above.

@@

```{r aggregate_features_5_eq}
features_top5 <- NULL
for(metric in names(boruta_results_eq)){
  features_top5 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}

x <- data.frame(top5 = sort(c(unique(features_top5))))
kable(x) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

@@

```{r aggregate_features_10_eq}
features_top10 <- NULL
for(metric in names(boruta_results_eq)){
  features_top10 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}

x <- data.frame(top10 = sort(c(unique(features_top10))))
kable(x) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```
